Formation and evolution of intermediate-mass ratio inspirals

### 2020-01-16 article.tex
Updates from Overleaf

\author{Manuel Arca Sedda and Pau Amaro-Seoane}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\affil{
Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
}

\begin{abstract}
%
% Motivation: Why do we care about the problem and the results?
% ==============================================================
%

>>>>

\author{Manuel Arca Sedda}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\author{Pau Amaro-Seoane}
\affil{Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\}
\affil{Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
Kavli Institute for Astronomy and }
\affil{Astrophysics, Beijing 100871, China\\
Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany}
\author{Xian Chen}
\begin{abstract}
%
% Motivation: Why do we care about the problem and the results?
% ==============================================================
%
